---
title: "Environmental Monitoring Trend Report"
subtitle: "Full Original Synthetic Dataset — Part 11-Aware Training Template"
format: html
params:
  report_id: "EM-TR-YYYY-###"
  report_period_start: "2025-01-01"
  report_period_end: "2025-06-29"
  approved_data_extract_id: "TRAINING-EXTRACT-001"
  code_release_id: "DEV-0.2.0"
---

```{r}
#| include: false
library(readr); library(dplyr); library(lubridate); library(ggplot2); library(digest); library(knitr); library(scales)
rendered_utc <- format(Sys.time(),tz="UTC",usetz=TRUE)
hash <- function(x) digest(file=x,algo="sha256")
```

# Dataset and compliance boundary

This package uses the **full original synthetic dataset**: 13 rooms, 180 days, 3,298 EM observations, and 229 personnel-monitoring observations. It includes production, RABS, sterility, development, corridors, gowning, airlocks, plus fictional trend signals.

**Training only:** this Quarto template is not a 21 CFR Part 11-compliant system and must not be used as a GMP record or for product-quality decisions. A compliant implementation requires a validated end-to-end process with approved intended use, access controls, secure time-stamped audit trails, retention/backup, change control, and validated electronic signatures.

Report ID: `r params$report_id`; extract: `r params$approved_data_extract_id`; code release: `r params$code_release_id`; rendered: `r rendered_utc`.

| Control area | Template support | Required organizational control |
|---|---|---|
| Intended performance | Visible parameters/calculations | Approved requirements, risk assessment, CSA/validation |
| Inputs | SHA-256 manifest | Approved extract, reconciliation, controlled source system |
| Audit trail | Render timestamp only | Secure independent time-stamped record audit trail |
| Access | None | Unique accounts, role-based access, review |
| Retention | Renderable output | Controlled archival of data, code, output, metadata, audit trail |
| E-signatures | None | Validated signature process linked to record |
| Change control | Release identifier | Controlled code/package/template changes |

# Import manifest

```{r}
paths <- c(EM="em_results.csv",Personnel="personnel_monitoring.csv",Sites="sampling_sites.csv",Rooms="rooms.csv",Events="facility_events.csv")
if(any(!file.exists(paths))) stop("Missing: ",paste(paths[!file.exists(paths)],collapse=", "))
manifest <- tibble::tibble(table=names(paths),file=unname(paths),sha256=unname(vapply(paths,hash,character(1))),bytes=unname(file.info(paths)$size),extract_id=params$approved_data_extract_id)
kable(manifest,caption="Retain manifest with controlled package")
em <- read_csv(paths["EM"],show_col_types=FALSE) |> mutate(sample_date=ymd(sample_date))
pm <- read_csv(paths["Personnel"],show_col_types=FALSE) |> mutate(sample_date=ymd(sample_date))
rooms <- read_csv(paths["Rooms"],show_col_types=FALSE)
events <- read_csv(paths["Events"],show_col_types=FALSE) |> mutate(across(contains("date"),ymd))
start <- ymd(params$report_period_start); end <- ymd(params$report_period_end)
em <- filter(em,sample_date>=start,sample_date<=end); pm <- filter(pm,sample_date>=start,sample_date<=end)
```

# Data-quality checks

```{r}
checks <- tibble(check=c("Duplicate EM IDs","Negative CFU","Not final approved","Alert or higher","Action or higher"),count=c(sum(duplicated(em$sample_id)),sum(em$result_cfu<0),sum(em$result_status!="Final Approved"),sum(em$result_cfu>=em$alert_limit_cfu),sum(em$result_cfu>=em$action_limit_cfu)))
kable(checks)
```

# EM trend summary

```{r}
summary <- summarise(em,samples=n(),positive=sum(result_cfu>0),positive_rate=percent(mean(result_cfu>0),accuracy=.1),alerts=sum(result_cfu>=alert_limit_cfu),actions=sum(result_cfu>=action_limit_cfu))
kable(summary)
room_summary <- em |> left_join(rooms,by="room_id") |> group_by(room_id,room_name,cleanroom_class,sample_method) |> summarise(samples=n(),total_cfu=sum(result_cfu),positive_rate=percent(mean(result_cfu>0),accuracy=.1),alerts=sum(result_cfu>=alert_limit_cfu),actions=sum(result_cfu>=action_limit_cfu),.groups="drop") |> arrange(desc(actions),desc(total_cfu))
kable(room_summary,caption="EM by room and method")
monthly <- em |> mutate(month=floor_date(sample_date,"month")) |> group_by(month,room_id) |> summarise(rate=mean(result_cfu>0),.groups="drop")
ggplot(monthly,aes(month,rate,color=room_id))+geom_line()+geom_point()+scale_y_continuous(labels=percent_format())+labs(x=NULL,y="Positive recovery rate",color="Room")+theme_minimal()
```

# Exceptions, flora, and personnel

```{r}
exceptions <- em |> filter(result_cfu>=alert_limit_cfu) |> arrange(desc(result_cfu),sample_date) |> select(sample_id,sample_date,room_id,site_id,sample_method,shift,operator_id,result_cfu,alert_limit_cfu,action_limit_cfu,event_classification,primary_isolate,result_status)
kable(exceptions,caption="Alert/action observations: human QC review required")
flora <- em |> filter(primary_isolate!="No Growth") |> group_by(primary_isolate) |> summarise(recoveries=n(),rooms=n_distinct(room_id),first=min(sample_date),last=max(sample_date),.groups="drop") |> arrange(desc(recoveries))
kable(flora,caption="Organism look-back")
pm_summary <- pm |> group_by(operator_id,room_id) |> summarise(samples=n(),positive=sum(result_cfu>0),alerts=sum(result_cfu>=alert_limit_cfu),actions=sum(result_cfu>=action_limit_cfu),.groups="drop") |> arrange(desc(actions),desc(positive))
kable(pm_summary,caption="Personnel-monitoring summary")
```

# Event context and documented review

```{r}
kable(filter(events,event_start_date<=end,event_end_date>=start),caption="Context only; no causality inferred")
```

Automated outputs are not quality conclusions. Document scientific assessment, investigations, CAPAs, action owners, and approvals in the validated quality system.

| Finding | Assessment/action | Owner | Due date | Deviation/CAPA ID | Closure evidence |
|---|---|---|---|---|---|
| | | | | | |

# Execution metadata

```{r}
print(list(rendered_utc=rendered_utc,report_id=params$report_id,code_release=params$code_release_id,R=R.version.string,packages=sapply(c("readr","dplyr","lubridate","ggplot2","digest"),function(x)as.character(packageVersion(x)))))
```
